**Preprinting Microbiology**

### 2017-02-21 submission/Schloss_PrePrints_mBio_2017.Rmd
Add reference to JID and updated ICMJE statement

***Acceptance of preprints by journals.*** An early controversy encountered by researchers interested in posting their work as preprints as a stage in disseminating their research was whether it constituted prior publication. The broad consensus at this point is that preprints do not constitute prior publication. This consensus is reflected in the current policies of journals that commonly publish microbiology research including those published by ASM, the Microbiology Society, International Society for Microbial Ecology, PLOS, the *Proceedings of the National Academy of Science*, *Science*, *Nature* and Cell press, which each take a generally permissive stance towards prior posting of preprints prior to submission. Considering the relatively fluid nature of many of these policies and the journals' specific policies, prospective authors should be aware of the positions taken by the journals where they may eventually submit their work. Comprehensive lists of journals' attitudes towards preprints are available online and are regularly updated [@PreprintPolicy; @Sherpa].

>>>>

***Acceptance of preprints by journals.*** An early controversy encountered by researchers interested in posting their work as preprints as a stage in disseminating their research was whether it constituted prior publication [@Angell1991]. The broad consensus of the International Committee of Medical Journal Editors and numerous journals is that preprints do not constitute prior publication [@ICMJE]. This consensus is reflected in the current policies of journals that commonly publish microbiology research including those published by ASM, the Microbiology Society, International Society for Microbial Ecology, PLOS, the *Proceedings of the National Academy of Science*, *Science*, *Nature*, *Journal of Infectious Diseases*, and Cell press, which each take a generally permissive stance towards prior posting of preprints prior to submission. Considering the relatively fluid nature of many of these policies and the journals' specific policies, prospective authors should be aware of the positions taken by the journals where they may eventually submit their work. Comprehensive lists of journals' attitudes towards preprints are available online and are regularly updated [@PreprintPolicy; @Sherpa].
